From Object Classification to Naming:\\ Modeling Entry-level Names for Real-world Objects

### 2019-12-10 papers/ACL2020/acl2020_main.tex
enthusiastic sentence at the end of the conclusions :-)
small fixes intro

\begin{document}
\maketitle
\begin{abstract}
Object detection and image classification models from Computer Vision are typically trained towards predicting labels of objects. 
Our goal is to extend such models to entry-level naming, where the task is to predict the natural name of an object that most humans would choose, instead of an \arbitrary name chosen by at best a few annotators. 
Based on large-scale, thoroughly verified object naming data from many annotators, we conduct an extensive analysis of the ability of object detection and classification models to account for entry-level object naming.
We show that standard object classification models ``spontaneously'' learn good entry-level names and perform better
on predicting entry-level than \arbitrary names, despite being trained on the latter, and that we can use transfer learning to train entry-level classifiers on the naming data. 
Our detailed error analysis reveals that models generally make more mistakes when human agreement is also low, with inadequate predictions due to bounding box issues being a major source of errors.
%Our analyses also demonstrate the challenges of collecting data of language phenomena that serves as a proxy for real-world situations in which the phenomenon of interest occurs.
%and systematically vary their training vocabulary. \cs{no diffs here with our setup of entry-levels only}
\end{abstract}

@@

\section{Conclusions}
\label{sec:conclusions}
In this paper, we have investigated instance-level entry-level naming of objects in images.
To the best of our knowledge, our work is the first to investigate entry-level naming on such a large-scale but thorougly verified empirical basis, 
as opposed to previous works that mostly adopted a class-level and/or strictly taxonomic view of naming.
For models in \lv, the complexity of human naming data we observed brings up an important question: how should a naming models best fine-tune and calibrate the \textit{vocabulary} of object detection and classification models from Computer Vision, in order to capture natural naming behavior?
We showed that the best way to achieve this is to first retrain an object detector on a large set of \arbitrary names and then fine-tune via transfer learning to entry-level names. 
In future work, we plan to develop this approach further and assess, e.g., how well the learned naming vocabulary generalizes for other, external datasets.
We also showed that naming data elicited for boxed objects comes with certain challenges, which have to be considered during evaluation (and potentially during modeling). 
%Bounding boxes are not always clear enough pointers to objects, and at the same time there is no clear line between other object mistakes (\textit{batter-helmet}), referential disagreements (\textit{bed-sleeping bag}, when the two visually overlap in the image), and valid alternatives (\textit{carpet-floor} can be a metonymy).
%Future work will need to address these challenges.

>>>>

\begin{document}
\maketitle
\begin{abstract}
Object detection and image classification models from Computer Vision are typically trained towards predicting labels of objects. 
Our goal is to extend such models to entry-level naming, where the task is to predict the natural name of an object that most humans would choose, instead of an \arbitrary name chosen by at best a few annotators. 
Based on large-scale, thoroughly verified object naming data from many annotators, we conduct an extensive analysis of the ability of object detection and classification models to account for entry-level object naming.
We show that standard object classification models ``spontaneously'' learn good entry-level names and perform better
on predicting entry-level than \arbitrary names, despite being trained on the latter, and that we can use transfer learning to train entry-level classifiers on the naming data. 
Our detailed error analysis reveals that models generally make more mistakes when human agreement is low, with inadequate predictions due to bounding box issues being a major source of errors.
%Our analyses also demonstrate the challenges of collecting data of language phenomena that serves as a proxy for real-world situations in which the phenomenon of interest occurs.
%and systematically vary their training vocabulary. \cs{no diffs here with our setup of entry-levels only}
\end{abstract}

@@

\section{Conclusions}
\label{sec:conclusions}
In this paper, we have investigated instance-level entry-level naming of objects in images.
To the best of our knowledge, our work is the first to investigate entry-level naming on such a large-scale but thorougly verified empirical basis, 
as opposed to previous works that mostly adopted a class-level and/or strictly taxonomic view of naming.
For models in \lv, the complexity of human naming data we observed brings up an important question: how should a naming models best fine-tune and calibrate the \textit{vocabulary} of object detection and classification models from Computer Vision, in order to capture natural naming behavior?
We showed that the best way to achieve this is to first retrain an object detector on a large set of \arbitrary names and then fine-tune via transfer learning to entry-level names. 
In future work, we plan to develop this approach further and assess, e.g., how well the learned naming vocabulary generalizes for other, external datasets.
We also showed that naming data elicited for boxed objects comes with certain challenges, which have to be considered during evaluation (and potentially during modeling).

More generally, we believe that the verified object naming data as well as our modeling approach affords tremendous opportunities to study factors affecting object naming that have not been studied to date, such as the prototypicality of the instance itself, or the effect of the visual context.

%Bounding boxes are not always clear enough pointers to objects, and at the same time there is no clear line between other object mistakes (\textit{batter-helmet}), referential disagreements (\textit{bed-sleeping bag}, when the two visually overlap in the image), and valid alternatives (\textit{carpet-floor} can be a metonymy).
%Future work will need to address these challenges.

### 2019-12-10 papers/ACL2020/introduction.tex
small fixes intro

Objects, being members of many categories, can be called by many names (e.g.,\ a duck can be called \name{duck, bird, animal} etc.). 
The task of \emph{object naming}---generating not just a formally correct but also an appropriate, \emph{natural} name for an object---is distinct from the closely related tasks of object detection and image classification (see below).
It has been studied in psycholinguistics~(e.g.,~\citet{Rosch1978}), but has received comparatively little attention in \langvis (\lv) and computational linguistics (CL) research.
We address the following question:\\
\fbox{\parbox{\columnwidth}{\textbf{Q:} Can standard object detection/image classification models (be fine-tuned to) exhibit human-like object naming behavior?}}\\\\
In particular, we test several models for their ability to predict \emph{entry-level names}, i.e., the names people prefer when calling a specific object (e.g.,~\name{bird} in Figure~\ref{fig:duck}, left image).
%% SHORTENING %% We wish to find out, for instance, whether different types of models or training regimes will tend towards different kinds of human-like errors in this regard.
A secondary contribution of this paper is instrumental: for a proper evaluation we must first augment an existing human object naming dataset (ManyNames, Anonymous, under review) with extensive quality control, the resulting data of which we also describe and make available with this paper.
\begin{figure}[t]
	\centering
	\small
	\begin{tabular}{p{3cm}p{3cm}}
		\centering
		\includegraphics[scale=0.15]{images/2327551_2960743_seed_ambiguous.png} &
		\includegraphics[scale=0.15]{images/2358126_805887_singleton_obj.png}\\
		bird\ (27),  duck\ (8) & duck (33), bird (3)\\
	\end{tabular}
	\caption{Different naming preferences (frequencies) for instances of the same \category \name{duck} in \mn.\label{fig:duck}}
\end{figure}

In \lv, object naming underlies virtually all tasks that model how speakers refer to objects in the world, such as image description or visual question answering.
\lv methods are generally based on object detection or image classification models from computer vision (CV) that were pre-trained towards predicting the single label of each object that is deemed correct by the dataset.
The labels used often seem unintuitive from a human perspective, e.g., some are very basic, natural names (\name{bus}) while others seem overly specific (\name{goblet, gyromitra}), cf.\ the label inventory of the ILSVRC challenges \cite{ILSVRC15}.
Pre-training on such labels can enable CV models to learn rich, discriminative visual feature representations which capture fine-grained differences in object appearances (e.g.,\ sharp-pointed vs. slightly pointed). 
But it raises the issue of whether these models could be directly used for more human-like object naming.
% Accordingly, these CV models are assessed by their ability to predict a single, in cases very specific, ground-truth label.

% By contrast, the goal of \lv object naming models is to predict the `natural' name of an object, i.e.,~the name a human could choose for the object instance.
Psycholinguistic studies have found that humans have a preference towards a particular name, defined as the \textit{entry-level name}, when naturally naming an object \cite{rosch1976basic,Rosch1978,jolicoeur1984pictures}. 
However, this research has traditionally focused on \categories and/or their prototypical/schematic depictions (e.g., \newcite{rossion2004revisiting}), as opposed to the situated instances in naturalistic images with which \lv is mostly concerned.
But humans may prefer different names for instances of the same \category (e.g., Figure~\ref{fig:duck}), and even disagree in their choice for the same instance (see also \citealt{graf2016animal}).
%% SHORTENING %% For example, in Figure~\ref{fig:duck} most people (27 out of 36) called the duck on the left \name{bird}, while \name{duck} was strongly preferred for the duck on the right.

@@

Our main contributions are to (i) run the \mn data through a rigorous annotation round to quantify both the adequacy of its names and the types of errors they contain, in order to (ii) test and compare object detection and image classification models at the task of \emph{instance-based, entry-level object naming}. 
More precisely, \mn enables us to define entry-level name as follows:\\
\fbox{\parbox{\columnwidth}{\textbf{Entry-level name:} the most common name given to an object instance according to ManyNames}}\\\\
We evaluate the effectiveness of different models on predicting these entry-level names, and our additional verification annotations enable us to understand the kinds of mistakes the models make (e.g.,~a `wrong' prediction may be a less preferred name as opposed to a true error).
We show that generic object classification models on their own (ResNet, Faster-RCNN and Bottom-up) already learn to provide entry-level names for objects, but also that they can transfer-learn on \mn, successfully using pre-trained features from object detection and image classification models to train entry-level naming models. 
%% SHORTENING %% \mw{Remark about the kinds of human errors, just as in the abstract, or some other more interesting teaser?}

>>>>

Objects, being members of many categories, can be called by many names (e.g.,\ a duck can be called \name{duck, bird, animal}, etc.). 
The task of \emph{object naming}---generating not just a formally correct but also an appropriate, \emph{natural} name for an object---is distinct from the closely related tasks of object detection and image classification (see below).
It has been studied in psycholinguistics~(e.g.,~\citealt{Rosch1978}), but has received comparatively little attention in \langvis (\lv) and computational linguistics (CL) research.
We address the following question:\\
\fbox{\parbox{\columnwidth}{\textbf{Q:} Can standard object detection/image classification models (be fine-tuned to) exhibit human-like object naming behavior?}}\\\\
In particular, we test several models for their ability to predict \emph{entry-level names}, i.e., the names people prefer when calling a specific object (e.g.,~\name{bird} in Figure~\ref{fig:duck}, left image).
%% SHORTENING %% We wish to find out, for instance, whether different types of models or training regimes will tend towards different kinds of human-like errors in this regard.
A second contribution of this paper is instrumental: for a proper evaluation we must first augment an existing human object naming dataset (ManyNames, Anonymous, under review) with extensive quality control, the resulting data of which we also describe here.%
\footnote{Data and code for this paper will be made available upon publication.}
\begin{figure}[t]
	\centering
	\small
	\begin{tabular}{p{3cm}p{3cm}}
		\centering
		\includegraphics[scale=0.15]{images/2327551_2960743_seed_ambiguous.png} &
		\includegraphics[scale=0.15]{images/2358126_805887_singleton_obj.png}\\
		bird\ (27),  duck\ (8) & duck (33), bird (3)\\
	\end{tabular}
	\caption{Different naming preferences (frequencies) for instances of the same \category \name{duck} in \mn.\label{fig:duck}}
\end{figure}

In \lv, object naming underlies virtually all tasks that model how speakers refer to objects in the world, such as image description or visual question answering.
\lv methods are generally based on object detection or image classification models from computer vision (CV) that were pre-trained towards predicting the single label of each object that is deemed correct by the dataset.
The labels used often seem unintuitive from a human perspective, e.g., some are very basic, natural names (\name{bus}) while others are much more specific (\name{goblet, gyromitra}), cf.\ the label inventory of the ILSVRC challenges \cite{ILSVRC15}.
Pre-training on such labels can enable CV models to learn rich, discriminative visual feature representations which capture fine-grained differences in object appearances (e.g.,\ sharp-pointed vs. slightly pointed). 
But it raises the issue of whether these models could be directly used for more human-like object naming.
% Accordingly, these CV models are assessed by their ability to predict a single, in cases very specific, ground-truth label.

% By contrast, the goal of \lv object naming models is to predict the `natural' name of an object, i.e.,~the name a human could choose for the object instance.
Psycholinguistic studies have found that humans have a preference towards a particular name, defined as the \textit{entry-level name}, when naturally naming an object \cite{rosch1976basic,Rosch1978,jolicoeur1984pictures}. 
However, this research has traditionally focused on \categories and/or their prototypical/schematic depictions (e.g., \citealt{rossion2004revisiting}), as opposed to the situated instances in naturalistic images with which \lv is mostly concerned.
But humans may prefer different names for instances of the same \category (e.g., Figure~\ref{fig:duck}), and even disagree in their choice for the same instance (see also \citealt{graf2016animal}).
%% SHORTENING %% For example, in Figure~\ref{fig:duck} most people (27 out of 36) called the duck on the left \name{bird}, while \name{duck} was strongly preferred for the duck on the right.

@@

Our main contributions are to (i) run the \mn data through a rigorous annotation round to quantify both the adequacy of its names and the types of errors they contain, in order to (ii) test and compare object detection and image classification models at the task of \emph{instance-based, entry-level object naming}. 
More precisely we define entry-level name as follows:\\
%, \mn enables us to define entry-level name as follows:\\
\fbox{\parbox{\columnwidth}{\textbf{Entry-level name:} the most common name given to an object instance according to ManyNames}}\\\\
We evaluate the effectiveness of different models on predicting these entry-level names, and our additional verification annotations enable us to understand the kinds of mistakes the models make (e.g.,~a `wrong' prediction may be a less preferred name as opposed to a true error).
We show that generic object classification models on their own already learn to provide entry-level names for objects, but also that they can transfer-learn on \mn, successfully using pre-trained features from object detection and image classification models to train entry-level naming models. 
%% SHORTENING %% \mw{Remark about the kinds of human errors, just as in the abstract, or some other more interesting teaser?}
